Old or Heavy?\\Decaying Gracefully with Age/Weight Shapes.

### 2019-02-21 papers/CADE19/paper.tex
convert no-best-awr figure to tabular format, add figure PDFs

This experiment was repeated on the whole TPTP problem set, excluding problems Vampire does not support, and problems which were not solved by the default mode in under a second for any AWR value.
The whole set yielded similar AWR data for 8,123 problems.
These data show that while there is no ``best'' AWR for the whole set (Figure \ref{fig:no-best-awr}), choosing a good AWR value for a problem is well-rewarded (Figure \ref{fig:optimal-awr-improvement}).

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{no-best-awr}
	\caption{The mean relative performance drop (in terms of activations compared to an optimal value) choosing a single AWR over an entire problem set causes. No setting is significantly ``better'' or ``worse'' than the others, but some have more variance in performance.}
	\label{fig:no-best-awr}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{random-walk}
	\caption{The AWR series that produced the lowest number of activations on a particular problem. This is a search strategy that a single fixed AWR cannot reproduce.}
	\label{fig:random-walk}
\end{figure}

>>>>

This experiment was repeated on the whole TPTP problem set, excluding problems Vampire does not support, problems which were not solved by the default mode in under a second for any AWR value, and problems solved in pre-processing.
The whole set yielded similar AWR data for 7,947 problems.
These data show that while there is no ``best'' AWR for the whole set (Figure \ref{fig:no-best-awr}), choosing a good AWR value for a problem is well-rewarded (Figure \ref{fig:optimal-awr-improvement}).

\begin{figure}
	\centering
	\begin{tabular}{l l l l l}
AWR & Minimum & Maximum & Mean & Standard Deviation\\
\hline
8:1 & 1.0 & 150.67 & 1.37 & 1.98\\
5:1 & 1.0 & 122.22 & 1.33 & 1.64\\
4:1 & 1.0 & 101.44 & 1.32 & 1.42\\
3:1 & 1.0 & 105.00 & 1.29 & 1.41\\
2:1 & 1.0 & 112.67 & 1.27 & 1.45\\
3:2 & 1.0 & 119.89 & 1.27 & 1.51\\
5:4 & 1.0 & 125.00 & 1.26 & 1.55\\
1 & 1.0 & 133.56 & 1.26 & 1.63\\
2:3 & 1.0 & 147.67 & 1.28 & 1.79\\
2 & 1.0 & 162.67 & 1.31 & 1.97\\
3 & 1.0 & 190.56 & 1.37 & 2.30\\
4 & 1.0 & 17.41 & 1.38 & 0.67\\
5 & 1.0 & 133.67 & 1.44 & 1.70\\
6 & 1.0 & 106.44 & 1.47 & 1.46\\
7 & 1.0 & 104.89 & 1.49 & 1.44\\
8 & 1.0 & 101.33 & 1.53 & 1.45\\
10 & 1.0 & 101.78 & 1.60 & 1.53\\
12 & 1.0 & 101.67 & 1.65 & 1.62\\
14 & 1.0 & 103.00 & 1.70 & 1.75\\
16 & 1.0 & 101.33 & 1.74 & 1.76\\
20 & 1.0 & 100.89 & 1.82 & 1.94\\
24 & 1.0 & 101.33 & 1.89 & 2.08\\
28 & 1.0 & 99.22 & 1.96 & 2.24\\
32 & 1.0 & 100.00 & 1.99 & 2.36\\
40 & 1.0 & 98.78 & 2.09 & 2.64\\
50 & 1.0 & 98.78 & 2.17 & 2.88\\
64 & 1.0 & 101.22 & 2.28 & 3.19\\
128 & 1.0 & 107.44 & 2.57 & 4.16\\
1024 & 1.0 & 222.01 & 2.83 & 7.55
	\end{tabular}
	\caption{The mean relative performance drop (in terms of activations compared to an optimal value) choosing a single AWR over an entire problem set causes. No setting is significantly ``better'' or ``worse'' than the others, but some have more variance in performance.}
	\label{fig:no-best-awr}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\textwidth]{random-walk}
	\caption{The AWR series that produced the lowest number of activations on a particular problem, smoothed in order to show the actual effect on proof search. This is a search strategy that a single fixed AWR cannot reproduce.}
	\label{fig:random-walk}
\end{figure}
